Figures

### 2020-08-03 inst/manuscript/figures.Rmd
Revised validation site analysis

>>>>

### Figure 6: Categorical map accuracy

### Figure 7: Segmentation statistics
```{r segstats, eval=FALSE}
data("top_label_data")
data("field_validation_stats")

human <- top_label_data$stats %>% 
  rename(hun = n, humu = Mean, hustd = StDev) %>% 
  select(-contains("id"))
machine <- field_validation_stats %>% 
  rename(man = n, mamu = Mean, mastd = StDev)
left_join(human, machine) %>% View()
machine %>% arrange(aoi) %>% View()
